---
title: "hw2"
author: "Elaine"
date: "1/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#R commands
#1.
(15-32)*5/9
(-10-32)*5/9
cel <- c(-9.44,-23.33)
cel

#2.
vec200 <- rep(c(1,0), length.out=200)
vec200

#3.
numPerfect <- floor(sqrt(1001))
numPerfect
?round

#Cars and Mileage
library(ggplot2)

#1.
head(mpg)
#hwympg <- mpg$hwy       code that didn't work
#hwympg
#sort(hwympg, decreasing = TRUE)
#a <- sort(hwympg, decreasing = TRUE)
#head(a)
#head(a,3)
b <-mpg[order(-mpg$hwy),]
b
top3 <- b[1:3,]
top3

#2.
View(mpg)
c <-mpg[mpg$class == 'compact',]
View(c)
numCompact <- c("47 Compact Models")
numCompact

#3.
ggplot(mpg, aes(x=cty, y=hwy)) + geom_point(shape=16, size=3) + 
  labs(x = "cty",y="hwy", title="Hwy vs Cty")+theme_bw()+
  theme(plot.title = element_text(hjust=0.5, size = rel(2)))+
  theme(axis.title.y = element_text(size = rel(1.4)))+
  theme(axis.title.x = element_text(size = rel(1.4)))+
  theme(axis.text.x = element_text(size = rel(1.6)))+
  theme(axis.text.y = element_text(size = rel(1.6)))

#I think there are so few points visible because many of the models have the same mpg for cty&hwy

#4.
#NONE OF THESE ARE WORKING!!

mpg[mpg$year == '2008', ]
mpg[mpg$year == '1999', ]
plot(mpg[mpg$year == '2008', ],mpg[mpg$year == '1999', ], col=mpg$year)

x <- mpg$year
y <- mpg$year
plot(x,y)
yr <- mpg$year
x[yr == '1999']
y[yr == '2008']
points(x[yr == '1999'], y[yr == '2008'], col='red')
plot(x[yr == '1999'], y[yr == '2008'])

```{r}
version
```